SCM plan for a troubling company

### 2012-01-17 article.tex
Lots of new content

In the identification process the different baselines must be identified. And more specifically who creates them, authorizes and verifies them, as well as the contents of them.\cite{cagan}

@@

@@

% Hur stor ccb?
% Hur rigorös CR kontroll?

\subsection{Branching Pattern}\printindex

The sporadic merges also gives a composition model but where the choices to make a composition of are very limited (the one we have since release or a dev. one) leading to collaboration problems.

The branching pattern we propose on the module level are to have each group to develop their module in  a developement branch and when it's \emph{reasonably} stable merge that to a

@@

The company releases a new product every 6 months which results we have several different products to maintain. A problem is that when a customer finds a bug or wants a new feature in a previous release The Problem Company can't reproduce this system or it's very hard. We will need something so we both know exactly what system the customer is using and so the programmer who will fix this problem easy can reconstruct the system to work on. A way to do this is to use a Bill of Material (BoM). When we release a product we then save information about the release such as which version every component is using, what hardware are we using, which features are implemented, test information etc.
When a customer has a problem with a certain release we can look at the BoM and know exactly what system the customer is using and we can start working on a fix right away.
We will also need version control of the product to get the correct version of each component in the program.
Everyone in the project must be able to find this BoM without too much effort and we need a system which makes it easy to setup a certain BoM on the computer which the programmer is using. Otherwise we loose the benefits with the BoM. The software which the company is producing are used on specific cellphones so we need to be able to reproduce the hardware somehow. This can be done by storing some cellphones but very often will the software not interact with the actual hardware and we can then focus on just software information. In the BoM we store both software information about our product but also the software the cellphone is using.

\section{Tools}
With eclipse they have several different add-ons which makes it hard for them to use another tool. An approach building upon this platform, in the from of another plug-in would therefore probably be the best solution.

>>>>

In the identification process the different baselines must be identified. And
more specifically who creates them, authorizes and verifies them, as well as the
contents of them \cite{cagan}.

@@

\subsection{Branching Pattern}

The sporadic merges also gives a composition model but where the choices to make
a composition of are very limited (the one we have since release or a dev. one)
leading to collaboration problems. The teams mostly needs to work against the
modules from the previous release but occasionally the need to test or work
against an intermediate version from another group exists. This is frequent
enough that the possiblility to do this is a requirement from the system.

While being able to use the developing version from another group is important
so is the need for the other group to be able to continue their work without
risk of breaking the build for the first. This can be a serious problem as even
if the group is extremely thorough with testing their changes before commit an
API change must now be synchronized with the other group wich slows development
down a lot.

The branching pattern we propose on the module level are to have each group to 
develop their module in  a developement branch and when it's time for a release
or synchronization with another team to create a branch for that. This is
described in \cite{StreamedLines} as \emph{deffered branching} pattern since
the development happens in mainline and is branched when needed for
incompatible changes. The releases can then be composed from those branches.
This pattern also avoids a too wide branching structure as the releases don't
have branches of their own and thus will minimize integration work needed when
mergin branches as the need for merges should be limited to backported
bugfixes from the mainline to the release branches.

The release branches are the groups releases versus the rest of the company and
used by the higher level of the CI hierarchy as items to compose releases of
the product from. As such they have a high need for stability and there would
need to be either a freeze of the development line prior to branching of the
release or the release branch have to be done quite some time before the
release to ensure the build is as stable as needed. The freeze necessarily
stops development of new features until the branch is made while the second
approach causes more integration between the branches to be made (as any bugs
found will need to be fixed on both branches). This decision can be made on a
release by release base depending on the current needs.

\subsubsection{Team variations}

The above describes the strategy main branches and patterns all groups should
use to facilitate working releases and collaboration between the groups. In
maintaining the development branch the groups are free to any strategy they
like inform of individual branches for each developer or feature that are then
merged with the main branch or just doing changes in such small increments that
commiting directly to the dev branch is feasible. The experience of individual
developers regarding version control is varied and some groups may benefit from
more advanced branching patterns that others.

@@

The exception to the above rule are changes that are planned to already
released branches where the needs to be involved since the changes need more
rigorous control as they carry more risk not going through the normal
freeze/testing that predates a release.

@@

The company releases a new product every 6 months which results in several
different products to maintain. A problem is that when a customer finds a bug or
wants a new feature in a previous release The Problem Company can't reproduce
this system or it's very hard. We will need something so we both know exactly
what system the customer is using and so the programmer who will fix this
problem easy can reconstruct the system to work on. A way to do this is to use a
Bill of Material (BoM). When we release a product we then save information about
the release such as which version every component is using, what hardware are we
using, which features are implemented, test information etc. When a customer has
a problem with a certain release we can look at the BoM and know exactly what
system the customer is using and we can start working on a fix right away. We
will also need version control of the product to get the correct version of each
component in the program. Everyone in the project must be able to find this BoM
without too much effort and we need a system which makes it easy to setup a
certain BoM on the computer which the programmer is using. Otherwise we loose
the benefits with the BoM. The software which the company is producing are used
on specific cellphones so we need to be able to reproduce the hardware somehow.
This can be done by storing some cellphones but very often will the software not
interact with the actual hardware and we can then focus on just
software information. In the BoM we store both software information about our
product but also the software the cellphone is using.

\section{Tools}

\subsection{Version control}

\subsubsection{Considerations}
The branching patterns chosen for the company on the higher level don't have to
much of a requirement for advanced branch handling but the backporting of fixes
from the development branch to the release branches is a quite frequent
workflow and should be made easy. The releases need to be built from a
collection of releases and this could either be made with some kind script
checking out the specified versions of the modules or version of the modules
with the configurations and script verions controlled as well or as just the
build script with the modules assed to this project as submodules if the tool
has support for this. The latter is preferred if possible. As the developers
are mostly using eclipse as development platform integration with this is a big
advantage. The company will not outsource or create another division for the
forseeable future so a single central repository would work well and the
network can be utilized at LAN-speeds.

\subsubsection{Choices}
From the above requirements the choices are quite open. Most tools support the
branching required and the cherry-picking of changes can be made in most tools
albeit more or less easily. The distributed nature is not needed as access to
the server is good and most developers are not experienced enough to take
advantages of local commits and branches, and those that are can work that way
against the server using personal branches.
